Stack Safety as a Security Property

### 2021-04-06 tex/main.tex
Couple little things (still getting started)

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  What is stack safety? Numerous mechanisms have been proposed to guard against
  attacks that corrupt the call stacks of running programs, including micro-policies
  implemented using metadata tagging mechanisms such as PIPE. But for specification
  these implementations largely appeal either to intuitive notions of the behavior
  of a stack, or to specific examples of bad behavior.
  %
  We propose a formal definition phrased in the technical terminology of language-based
  security---as a combination of an integrity property (a caller's stack frame is
  invariant over calls) and a confidentiality property (callees lack knowledge of the
  contexts of their calls). These combine with a straightforward well-bracketedness
  condition on the program's control flow that ensures that callers and callees remain
  meaningfully distinct.
  %
  While our formalism is informed by the PIPE implementation, the primary properties reflect
  general principles of stack safety. We define additional properties tailored for specific
  contexts: a stronger property amenable to efficient testing and a weaker one that is
  approximated by more efficient, lazy policies.

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
\bcp{How about ``Stack Safety {\em is} a Security Property''?}
  What is stack safety? The phrase has been used to describe the protections
  offered by a variety of mechanisms for guarding against
  attacks that corrupt the call stacks of running programs, including micro-policies
  implemented using metadata tagging mechanisms such as PIPE. But for specification
  these implementations largely appeal either to intuitive notions of the behavior
  of a stack, or to specific examples of bad behavior.
  %
  We propose a formal definition phrased in the technical terminology of language-based
  security---as a combination of an integrity property (a caller's stack frame is
  invariant over calls) and a confidentiality property (callees lack knowledge of the
  contexts of their calls). These combine with a straightforward well-bracketedness
  condition on the program's control flow that ensures that callers and callees remain
  meaningfully distinct.
  %
  While our formalism is informed by the PIPE implementation, the primary properties reflect
  general principles of stack safety. We define additional properties tailored for specific
  contexts: a stronger property amenable to efficient testing and a weaker one that is
  approximated by more efficient, lazy policies.
